---
title: "Introduction to finna"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to finna}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

This vignette provides an overview of how to use the finna package.

To make a simple search use the following code.

**N.B** In the search_finna() default limit of 100 records is being used. Specify 'limit' argument for more records.


```{r message = FALSE, warning = FALSE}
library(finna)
record <- search_finna("sibelius")
print(record)
```

## Searching as subject

```{r message = FALSE, warning = FALSE}
library(finna)
record <- search_finna(query = '"orkesterimusiikki"', type = "Subject", lng = "en-gb")
print(record)
```
## Bulk search 
 
 I we need a bulk download we use
`search_finna("sibelius", limit = Inf)` where we add the term `limit = Inf`.

## Free text search
```{r message = FALSE, warning = FALSE}
library(finna)
result <- search_finna("Jansson Tove")
print(result)
```

## Search phrase examples
```{r message = FALSE, warning = FALSE}
library(finna)
phrase <- search_finna("bicycle")
print(phrase)
```

## Combining search terms

### AND
Use the AND operator to yield search results which feature every term in the 
search field. If you write several words into the search field and separate 
them with a space, the space will function as the AND operator.

Example 1
```{r message = FALSE, warning = FALSE}
library(finna)
Combination <- search_finna("nutrition AND (diet OR lifestyle)")
print(Combination)
```

Example 2
For example, these two searches will yield the same results:

```{r message = FALSE, warning = FALSE}
library(finna)
no_Combination <- search_finna("Karisto Seppälä")
print(no_Combination)
```

```{r message = FALSE, warning = FALSE}
library(finna)
Combination_AND <- search_finna("Karisto AND Seppälä")
print(Combination_AND)
```

### OR

The OR operator expands your search results. The results will show material that
feature at least one of the search terms you indicated. For example, if you are
looking for information on the Eastern Orthodox Church:

```{r message = FALSE, warning = FALSE}
library(finna)
Combination_OR <- search_finna("Eastern Orthodoxy” OR “Orthodox Church")
print(Combination_OR)
```

Using the OR operator will return results that feature one or more of your 
search terms.This example search will find results relating to farms or farming:

```{r message = FALSE, warning = FALSE}
library(finna)
phrase <- search_finna("farm OR farming")
print(phrase)
```

### NOT

```{r message = FALSE, warning = FALSE}
library(finna)
Combination_OR <- search_finna("surrealism NOT (painting OR “visual arts”)")
print(Combination_OR)
```

### Search operators + and !-
In addition to the most common Boolean operators (AND, OR, NOT), Finna uses the + and !- operators.

### +

```{r message = FALSE, warning = FALSE}
library(finna)
search_oper <- search_finna("+economics Keynes”)")
print(search_oper)
```

### !-

```{r message = FALSE, warning = FALSE}
library(finna)
search_oper <- search_finna("economics !-Keynes”)")
print(search_oper)
```

#### NB! The !- operator cannot be used in single-word searches.

For example, the following search will yield no results:

```{r message = FALSE, warning = FALSE}
library(finna)
search_oper <- search_finna("!-economics”)")
print(search_oper)
```
### The use of wildcards in search terms

### Use of wildcards

NB! The wildcard symbols (* and ?) cannot be the first character of a search term

### * (Asterisk)
The search term may be truncated at the end with an asterisk. For example, to 
find search results for the terms competition, competitions, competitor and 
competitiveness, use the search term:

Example 1

```{r message = FALSE, warning = FALSE}
library(finna)
search_Asterisk <- search_finna("competit*”)")
print(search_Asterisk)
```

The asterisk may also be used in the middle of a search term to replace one or 
more characters. For example, to search for both the terms color and colour, 
use the search term:

Example 2

```{r message = FALSE, warning = FALSE}
library(finna)
search_Asterisk <- search_finna("colo*r”)")
print(search_Asterisk)
```

### ? (Question Mark)
The question mark symbol replaces one character in the search term, enabling 
the use of different word forms.
For example, to find results for both the terms woman and women, use the search term:

### ISBN/ISSN search

```{r message = FALSE, warning = FALSE}
library(finna)
ISBN <- search_finna("978-951-31-6583-3")
print(ISBN)
```

## Sorting 

### To search all related in descending order

```{r message = FALSE, warning = FALSE}
record <- search_finna("sibelius", sort = "main_date_str des")
print(record)
```
### To search all related in ascending order

```{r message = FALSE, warning = FALSE}
record <- search_finna("sibelius", sort = "main_date_str asc")
print(record)
```

### To search Last modified

```{r message = FALSE, warning = FALSE}
record <- search_finna("sibelius", sort = "last_indexed desc")
print(record)
```

### To search Last added

```{r message = FALSE, warning = FALSE}
record <- search_finna("sibelius", sort = "first_indexed desc")
print(record)
```

### Fine-tuning your search

#### Fuzzy search

Fuzzy search will also yield results that feature words which are similar to your search term.

The search operator ~ will perform a fuzzy search when it is used as the final character of a single-word search.

For example, a fuzzy search with the word roam will also return results with the words foam and roams.

```{r message = FALSE, warning = FALSE}
fuzzy_search <- search_finna("roam~")
print(fuzzy_search)
```

#### Proximity search

Proximity searches look for material in which the search terms are within a 
specified distance, but not necessarily one after the other.

```{r message = FALSE, warning = FALSE}
fuzzy_search <- search_finna("economics Keynes~10")
print(fuzzy_search)
```

## Advanced search: to see available online


```{r message = FALSE, warning = FALSE}
record <- search_finna("sibelius", filters = c("free_online_boolean:1"))
print(record)
```

### search image

```{r message = FALSE, warning = FALSE}
record <- search_finna("sibelius", filters = c('~media_type_str_mv:"0/image/"'))
print(record)
```

### Audio book

```{r message = FALSE, warning = FALSE}
record <- search_finna("sibelius", filters = c('~format:"1/Book/AudioBook/"'))
print(record)
```

### Year of manufacture

```{r message = FALSE, warning = FALSE}
record <- search_finna("sibelius", filters = c('search_daterange_mv:"overlap|[-5000 TO 5000]"'))
print(record)
```

### Search using Geofilter syntax (Geographical region)

```{r message = FALSE, warning = FALSE}
record <- search_finna("trump", filters = c('{!geofilt sfield=location_geo pt=61.663987171517796,24.17263895273209 d=212.53603751769646}'))
print(record)
```

### geofilter ouside of finland


```{r message = FALSE, warning = FALSE}
record <- search_finna("trump", filters = c('{!geofilt sfield=location_geo pt=39.3130504637139,-76.33021295070648 d=281.83790818401854}'))
print(record)
```

### Narrowing the search 

When narrowing search you can  use codes as a combination as follows

```{r message = FALSE, warning = FALSE}
record <- search_finna("trump", filters = c('{!geofilt sfield=location_geo pt=61.663987171517796,24.17263895273209 d=212.53603751769646},author_facet:"Häkkinen,Hannu"'))
print(record)
```


### specific search 

```{r message = FALSE, warning = FALSE}
record <- search_finna("era:'2010-luku'", filters = c('building:"0/3AMK/"'))

```

### search without removing duplication

In order to search data without removing duplication
[example](https://www.finna.fi/Search/Results?dfApplied=1&lookfor=era%3A%222010-luku%22&type=AllFields&filter[]=~building%3A%220%2F3AMK%2F%22&filter[]=finna.deduplication:%220%22)

```{r message = FALSE, warning = FALSE}
record <- search_finna('era:"2010-luku"', filters = c('~building:"0/3AMK/"', 'finna.deduplication:"1"'))
print(record)
```
We can confirm this as follows by checking the count

```{r message = FALSE, warning = FALSE}
record <- search_finna('era:"2010-luku"', filters = c('~building:"0/3AMK/"', 'finna.deduplication:"1"'))
result_count <- attr(record, "result_count")
print(result_count)
```

Removing duplication can be done as follows

```{r message = FALSE, warning = FALSE}
record <- search_finna('era:"2010-luku"', filters = c('~building:"0/3AMK/"', 'finna.deduplication:"0"'))
print(record)
```

To confirm this we can check the count 

```{r message = FALSE, warning = FALSE}
record <- search_finna('era:"2010-luku"', filters = c('~building:"0/3AMK/"', 'finna.deduplication:"0"'))
result_count <- attr(record, "result_count")
print(result_count)
```

# Search Finna with multiple filters 
To find scholarly journals and digital repository materials regarding music 

```{r message = FALSE, warning = FALSE}
results <- search_finna(
  query = "musiikki OR taide OR tanssi OR teatteri",
  filters = c(
    '~hierarchy_parent_title:"Institutional Repository"',
    '~format_ext_str_mv:"1/Thesis/Gradu/"',
    '~format_ext_str_mv:"1/Thesis/Masters/"',
    '~format_ext_str_mv:"1/Thesis/MastersPolytechnic/"',
    '~format_ext_str_mv:"1/Thesis/Thesis/"',
    '~format_ext_str_mv:"1/Thesis/Licentiate/"',
    '~format_ext_str_mv:"0/OtherText/"',
    '~format_ext_str_mv:"0/Journal/"',
    '~format_ext_str_mv:"0/Book/"',
    'free_online_boolean:"1"'
  ),
  type = "AllFields",
  lng = "en-gb",
  prettyPrint = TRUE
)

# Print the results
print(results)
```
