---
title: "Fennica in Finna"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fennica in Finna}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Fennica 

To search Fennica data in Finna

```{r}
library(finna)
fennica <- search_finna("*",filters=c('collection:"FEN"'))
print(fennica)
```

## Bulk data

In order to download the whole data we can add the parameter `limit = Inf`
as `search_finna("*",filters=c('collection:"FEN"'), limit = Inf)`

## Checking the total counts

search the whole data and it total search of counts in the the interval between 
some years for example between the years 1809-1917 as follows:

```{r}
library(finna)
fennica <- search_finna("*",filters = c('collection:"FEN"', 'search_daterange_mv:"[1809 TO 1918]"'))
print(fennica)
```

we can check the whole data count

```{r}
library(finna)
fennica <- search_finna("*",filters = c('collection:"FEN"', 'search_daterange_mv:"[1809 TO 1918]"'))
result_count <- attr(fennica, "result_count")
print(result_count)
```

## Visualization for fennica

We can use any of the functions provided to visualize the data 
```{r}
library(finna)
fennica <- search_finna("*",filters = c('collection:"FEN"', 'search_daterange_mv:"[1809 TO 1918]"'))
refined_data <- refine_metadata(fennica)
visualize_author_distribution(refined_data)
```

```{r}
fennica <- search_finna("*",filters = c('collection:"FEN"', 'search_daterange_mv:"[1809 TO 1918]"'))
refined_data <- refine_metadata(fennica)
visualize_word_cloud(refined_data, "Title")
```
