---
title: "Fennica in Finna"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fennica in Finna}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Fennica 

To search Fennica data in Finna

**N.B** In the search_finna() default limit of 100 records is being used. Specify 'limit' argument for more records.

```{r message = FALSE, warning = FALSE}
library(finna)
fennica <- search_finna("*",filters=c('collection:"FEN"'))
print(fennica)
```

## Bulk data

In order to download the whole data we can add the parameter `limit = Inf`
as `search_finna("*",filters=c('collection:"FEN"'), limit = Inf)`

## Checking the total counts

search the whole data and it total search of counts in the the interval between 
some years for example between the years 1809-1917 as follows:

```{r message = FALSE, warning = FALSE}
library(finna)
fennica <- search_finna("*",filters = c('collection:"FEN"', 'search_daterange_mv:"[1809 TO 1918]"'))
print(fennica)
```

we can check the whole data count

```{r message = FALSE, warning = FALSE}
library(finna)
fennica <- search_finna("*",filters = c('collection:"FEN"', 'search_daterange_mv:"[1809 TO 1918]"'))
result_count <- attr(fennica, "result_count")
print(result_count)
```

## Visualization for fennica

We can use any of the functions provided to visualize the data 
```{r message = FALSE, warning = FALSE}
library(finna)
fennica <- search_finna("*",filters = c('collection:"FEN"', 'search_daterange_mv:"[1809 TO 1918]"'))
refined_data <- refine_metadata(fennica)
visualize_author_distribution(refined_data)
```

```{r message = FALSE, warning = FALSE}
fennica <- search_finna("*",filters = c('collection:"FEN"', 'search_daterange_mv:"[1809 TO 1918]"'))
refined_data <- refine_metadata(fennica)
visualize_word_cloud(refined_data, "Title")
```

To search for specific fields like author information, publication details, and call numbers 
using `search_finna`, you can use Finna's **field-specific search filters**. Finna allows 
you to search in different fields by specifying the `type` parameter or adding filters. 
Here's how you can modify the `search_finna` function to query these fields:

### 1. **Search for Author Information:**

   - You can use the `type = "Author"` option to specifically search for records by author.

```{r message = FALSE, warning = FALSE}
library(finna)
record <-search_finna(query = "Jean Sibelius", type = "Author")
record
```

Alternatively, you can apply filters to search for authors using the `filters` parameter:

```{r message = FALSE, warning = FALSE}
record <- search_finna(query = "Jean Sibelius", filters = c('author:"Jean Sibelius"'))
record
```

