---
title: "Fennica in Finna"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fennica in Finna}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Fennica 

To search Fennica data in Finna

**N.B** In the search_finna() default limit of 100 records is being used. Specify 'limit' argument for more records.

```{r message = FALSE, warning = FALSE}
library(finna)
fennica <- search_finna("*",filters=c('collection:"FEN"'))
print(fennica)
```

## Bulk data

In order to download the whole data we can add the parameter `limit = Inf`
as `search_finna("*",filters=c('collection:"FEN"'), limit = Inf)`

## 19th century fennica data

search the whole data and it total search of counts in the the interval between 
some years for example between the years 1809-1917 as follows:

```{r message = FALSE, warning = FALSE}
library(finna)
fennica <- search_finna("*",filters = c('collection:"FEN"', 'search_daterange_mv:"[1808 TO 1918]"'))
print(fennica)
```

we can check the whole data count

```{r message = FALSE, warning = FALSE}
library(finna)
fennica <- search_finna("*",filters = c('collection:"FEN"', 'search_daterange_mv:"[1809 TO 1918]"'))
result_count <- attr(fennica, "result_count")
print(result_count)
```

## Visualization for fennica

We can use any of the functions provided to visualize the data 
```{r message = FALSE, warning = FALSE, fig.alt = "visualize author distribution"}
library(finna)
fennica <- search_finna("*",filters = c('collection:"FEN"', 'search_daterange_mv:"[1809 TO 1918]"'))
refined_data <- refine_metadata(fennica)
```

```{r message = FALSE, warning = FALSE, fig.alt = "visualize word cloud"}
library(finna)
library(ggplot2)
fennica <- search_finna("*",filters = c('collection:"FEN"', 'search_daterange_mv:"[1809 TO 1918]"'))
refined_data <- refine_metadata(fennica)
top_plot(refined_data, field = "Year") +
  xlab("Publication Year") +  # Custom X-axis label
  ylab("Number of Publications")  # Custom Y-axis label

```


### Notes:
- **Filters**: The filters need to match the exact field names used in Finna's API. You can find these field names in the API documentation or by looking at the response from the API [here](https://www.kiwi.fi/display/Finna/Kenttien+mappaukset+eri+formaateista+Finnan+indeksiin).
- **Call Number Search**: Ensure that the call numbers are correctly formatted according to the library's classification system (e.g., [YKL in Finland](https://finto.fi/ykl/fi/?clang=en)).
  
This way, you can extract specific metadata like authors, publication years, and call numbers using the `search_finna` function.
