---
title: "Fennica in Finna"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fennica in Finna}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Fennica 

To search Fennica data in Finna

**N.B** In the search_finna() default limit of 100 records is being used. Specify 'limit' argument for more records.

```{r message = FALSE, warning = FALSE}
library(finna)
fennica <- search_finna("*",filters=c('collection:"FEN"'))
print(fennica)
```

## Bulk data

In order to download the whole data we can add the parameter `limit = Inf`
as `search_finna("*",filters=c('collection:"FEN"'), limit = Inf)`

## 19th century fennica data

search the whole data and it total search of counts in the the interval between 
some years for example between the years 1809-1917 as follows:

```{r message = FALSE, warning = FALSE}
library(finna)
fennica <- search_finna("*",filters = c('collection:"FEN"', 'search_daterange_mv:"[1808 TO 1918]"'))
print(fennica)
```

we can check the whole data count

```{r message = FALSE, warning = FALSE}
library(finna)
fennica <- search_finna("*",filters = c('collection:"FEN"', 'search_daterange_mv:"[1809 TO 1918]"'))
result_count <- attr(fennica, "result_count")
print(result_count)
```

## Visualization for fennica

We can use any of the functions provided to visualize the data 
```{r message = FALSE, warning = FALSE, fig.alt = "visualize author distribution"}
library(finna)
fennica <- search_finna("*",filters = c('collection:"FEN"', 'search_daterange_mv:"[1809 TO 1918]"'))
refined_data <- refine_metadata(fennica)
```

```{r message = FALSE, warning = FALSE, fig.alt = "visualize word cloud"}
fennica <- search_finna("*",filters = c('collection:"FEN"', 'search_daterange_mv:"[1809 TO 1918]"'))
refined_data <- refine_metadata(fennica)
```

To search for specific fields like author information, publication details, and call numbers 
using `search_finna`, you can use Finna's **field-specific search filters**. Finna allows 
you to search in different fields by specifying the `type` parameter or adding filters. 
Here's how you can modify the `search_finna` function to query these fields:

### 1. **Search for Author Information:**

   - You can use the `type = "Author"` option to specifically search for records by author.

```{r message = FALSE, warning = FALSE}
library(finna)
record <-search_finna(query = "Jean Sibelius", type = "Author")
record
```

Alternatively, you can apply filters to search for authors using the `filters` parameter:

```{r message = FALSE, warning = FALSE}
record <- search_finna(query = "Jean Sibelius", filters = c('author:"Jean Sibelius"'))
record
```

### 2. **Search for Publication Information:**

   If you want to search for publication information such as the publication date or publisher, you can use `type = "Title"` or `type = "AllFields"` and then apply filters:

   - For specific years, you can use the `search_daterange_mv` filter:

     ```r
     search_finna(query = "Sibelius", filters = c('search_daterange_mv:"[2000 TO 2020]"'))
     ```

   - To search by publisher, you can add a filter for the publisher name:

     ```r
     search_finna(query = "Sibelius", filters = c('publisher:"Ondine"'))
     ```

### 3. **Search by Call Numbers:**

   Call numbers are used to classify items in libraries. To search by call number, you can add a filter for `callnumber-search` or `callnumber`:

   ```r
   search_finna(query = "Sibelius", filters = c('callnumber-search:"78.54"'))
   ```

   This will return results where the call number is `78.54` (which is typically used for orchestral music).

### Example Using Multiple Filters:
You can combine these search types and filters to make more complex queries. For instance, to search for works by **Jean Sibelius** published between **2000 and 2020** with the call number **78.54**:

```r
search_finna(
  query = "Sibelius",
  filters = c('author:"Jean Sibelius"', 'search_daterange_mv:"[2000 TO 2020]"', 'callnumber-search:"78.54"')
)
```

### Code Overview:

```r
# Author search example
search_finna(query = "Jean Sibelius", type = "Author")

# Search for works by author with publication date range
search_finna(query = "Jean Sibelius", filters = c('search_daterange_mv:"[2000 TO 2020]"'))

# Search for works by call number
search_finna(query = "Sibelius", filters = c('callnumber-search:"78.54"'))

# Combine author, publication date, and call number filters
search_finna(
  query = "Sibelius",
  filters = c('author:"Jean Sibelius"', 'search_daterange_mv:"[2000 TO 2020]"', 'callnumber-search:"78.54"')
)
```

### Notes:
- **Filters**: The filters need to match the exact field names used in Finna's API. You can find these field names in the API documentation or by looking at the response from the API [here](https://www.kiwi.fi/display/Finna/Kenttien+mappaukset+eri+formaateista+Finnan+indeksiin).
- **Call Number Search**: Ensure that the call numbers are correctly formatted according to the library's classification system (e.g., YKL in Finland).
  
This way, you can extract specific metadata like authors, publication years, and call numbers using the `search_finna` function.
