---
title: "Fennica Authors in Kanto"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fennica Authors in Kanto}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Introduction

This document provides an example usage of the search_fennica_authors() function, which links authors from the Fennica catalog to their respective Kanto IDs in Finto's 'Finaf' vocabulary. The function helps enrich metadata for bibliographic records.

```{r message = FALSE, warning = FALSE}
suppressMessages(suppressWarnings({
  if (!requireNamespace("devtools", quietly = TRUE)) {
    install.packages("devtools", quiet = TRUE)
  }
  devtools::install_github("ake123/finto", quiet = TRUE)
}))
```

After downloading the package  we select the columns `id`, `Title` and `Author`

```{r message = FALSE, warning = FALSE}
library(finna)
library(finto)
library(dplyr)

data("fennica_subset",package = "finna")
fennica_subset <- tail(fennica_subset)
knitr::kable(fennica_subset,caption = "few selected fennica data")
```

So the processed output of the retrieved finto/kanto data can be found using the provided code below.

```{r message = FALSE, warning = FALSE}
authors_df <- finto::process_and_fetch_kanto_info(fennica_subset)
knitr::kable(authors_df, caption = "Authors Data Frame from kanto")
```







