---
title: "Overview of Finna Collection"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of Finna Collection}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Introduction

This section helps us to have a general overview of the general collection in Finna. For this purpose we use a separate function `fetch_finna`.
This document demonstrates the use of the `fetch_finna` function to retrieve data from the Finna API with various queries and parameters.


## Example 1: Fetching EAD Records

```{r message = FALSE, warning = FALSE}
library(finna)
result <- fetch_finna(
  query = "record_format:ead",
  limit = 0,
  facets = "building",
  lng = "fi",
  prettyPrint = TRUE
)
print(result)
```


## Example 2: Fetching EAD3 Records

```{r message = FALSE, warning = FALSE}
library(finna)
result <- fetch_finna(
  query = "record_format:ead3",
  limit = 0,
  facets = "building",
  lng = "fi",
  prettyPrint = TRUE
)
print(result)
```


## Conclusion

This document provides examples of how to use the `fetch_finna` function for retrieving various types of records from the Finna API. The tibbles contain structured data for further analysis.


