---
title: "Refine finna metadata"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Refine finna metadata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

The purpose of the ` refine_metadata()` function is to:

- **Ensure completeness** by filling in missing values with placeholder text.
- **Standardize key metadata fields** for easier analysis.
- **Select only the most relevant fields**, simplifying the dataset.

This refinement process makes the metadata more consistent and user-friendly, reducing potential issues in subsequent analysis or reporting.


```{r message = FALSE, warning = FALSE}
library(finna)
library(ggplot2)
sibelius_data <- search_finna("sibelius")
refined_data <- refine_metadata(sibelius_data)
print(refined_data)
```

### **Analyze using ` analyze_metadata()` Function**

```{r message = FALSE, warning = FALSE}
sibelius_data <- search_finna("sibelius")
refined_data <- refine_metadata(sibelius_data)
analysis_results <- analyze_metadata(refined_data)
print(analysis_results)
```

### 1. **Applying the `visualize_year_distribution()` Function**

```{r message = FALSE, warning = FALSE, fig.alt = "year_distribution"}
sibelius_data <- search_finna("sibelius")
refined_data <- refine_metadata(sibelius_data)
analysis_results <- analyze_metadata(refined_data)
#visualize_year_distribution(analysis_results$year_distribution)
top_plot(analysis_results$author_distribution, field = "n") +
    xlab("Frequency") +  # Custom X-axis label
    ylab("Number of Authors")  # Custom Y-axis label
```

### 1. yearly distribution using top_plot()
```{r message = FALSE, warning = FALSE, fig.alt = "year distribution line"}
library(finna)
sibelius_data <- search_finna("sibelius")
refined_data <- refine_metadata(sibelius_data)
#visualize_year_distribution_line(refined_data)
top_plot(refined_data, field = "Year") +
  xlab("Publication Year") +  # Custom X-axis label
  ylab("Number of Publications")  # Custom Y-axis label

```



