---
title: "Refine, integrate and analyse Finna metadata"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Refine, integrate and analyse Finna metadata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

This vignette provides an overview of how to use the finna package.

### **Refine using ` refine_metadata()` function**

```{r}
library(finna)
sibelius_data <- search_finna("sibelius")
refined_data <- refine_metadata(sibelius_data)
print(refined_data)
```

### **integrate using ` integrate_metadata()` Function**


```{r}
finna_data <- search_finna("sibelius")
other_data <- tibble::tibble(
  Title = c("Sibelius Symphony No. 5", "Finlandia", "Valse Triste"),
  Rating = c(5, 4, 3)
)
integrated_data <- integrate_metadata(finna_data, other_data, key = "Title")
print(integrated_data)
```


### **Analyze using ` analyze_metadata()` Function**

```{r}
sibelius_data <- search_finna("sibelius")
refined_data <- refine_metadata(sibelius_data)
analysis_results <- analyze_metadata(refined_data)
print(analysis_results)
```

### 1. **Applying the `visualize_year_distribution()` Function**

```{r}
sibelius_data <- search_finna("sibelius")
refined_data <- refine_metadata(sibelius_data)
analysis_results <- analyze_metadata(refined_data)
visualize_year_distribution(analysis_results$year_distribution)
```

### 1.1 Line plot of yearly distribution
```{r}
library(finna)
sibelius_data <- search_finna("sibelius")
refined_data <- refine_metadata(sibelius_data)
visualize_year_distribution_line(refined_data)
```

### 2. **Applying the `visualize_top_20_titles()` Function**

This function will visualize the top 20 titles from your dataset.

```{r}
# Assuming you have a tibble with Finna metadata called `refined_data`
top_20_titles_plot <- visualize_top_20_titles(refined_data)

# To display the plot
print(top_20_titles_plot)
```

### 2.1 Visualize Heatmap of Titles by Year
```{r warning=FALSE}
library(finna)
sibelius_data <- search_finna("sibelius")
refined_data <- refine_metadata(sibelius_data)
visualize_title_year_heatmap(refined_data)
```

### 3. **Applying the `visualize_format_distribution()` Function**

This function visualizes the distribution of the records by format.

```{r}
# Plot the format distribution
format_distribution_plot <- visualize_format_distribution(refined_data)

# To display the plot
print(format_distribution_plot)
```
### 3.1 Visualize Format Distribution as Pie Chart
```{r}
library(finna)
sibelius_data <- search_finna("sibelius")
refined_data <- refine_metadata(sibelius_data)
visualize_format_distribution_pie(refined_data)
```

### 4. **Applying the `visualize_library_distribution()` Function**

This function shows the distribution of the records by library.

```{r}
# Plot the library distribution
library_distribution_plot <- visualize_library_distribution(refined_data)

# To display the plot
print(library_distribution_plot)
```
### 4.1 **Visualize Correlation Between Formats and Libraries**

This function shows the distribution of the records by library.

```{r}
library(finna)
sibelius_data <- search_finna("sibelius")
refined_data <- refine_metadata(sibelius_data)
visualize_format_library_correlation(refined_data)
```


### 5. **Applying the `visualize_author_distribution()` Function**

This function visualizes the distribution of the records by author.

```{r}
# Plot the author distribution
author_distribution_plot <- visualize_author_distribution(refined_data)

# To display the plot
print(author_distribution_plot)
```

### 6. **Applying the `visualize_subject_distribution()` Function**

This function visualizes the distribution of the records by subject.

```{r}
# Plot the subject distribution
subject_distribution_plot <- visualize_subject_distribution(refined_data)

# To display the plot
print(subject_distribution_plot)
```
### 6.1 **Visualize Word Cloud of Titles or Subjects**

This function visualizes the distribution of the records by subject.

```{r}
music_data <- search_finna("music")
refined_data <- refine_metadata(music_data)
visualize_word_cloud(refined_data, "Title")
```
