---
title: "Viola in Finna"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Viola in Finna}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
[Viola](https://kansalliskirjasto.finna.fi/Content/viola) is the Finnish national discography and the national bibliography of sheet music, maintained by the National Library of Finland. It contains information on Finnish music recordings and sheet music, as well as music archives included in the National Library's collections.

This R Markdown document provides a comprehensive guide to querying and analyzing Viola collection data using the Finna API and the `fetch_viola_records` function.

## Viola Collection in Finna

The `fetch_viola_records` function allows batch processing of data from the Viola collection in Finna, across multiple year ranges, and handles records without date information.

### Example Usage

#### Fetch Data Across Year Ranges

The following example fetches data from the Viola collection for the year ranges: 0–1699, 1700–1799, and 1800–1899. 

```{r message = FALSE, warning = FALSE}
library(finna)

# Fetch records
results <- fetch_viola_records(
  base_query = "*",
  base_filters = c('collection:"VIO"'), # Filters for the Viola collection
  year_ranges = list(c(0,1699),c(1700,1799),c(1800,1899)),           # Year ranges to query
  include_na = TRUE,                   # Include records with missing dates
  limit_per_query = 100000,              # Maximum records per query
  total_limit = Inf,                 # Overall record limit
  delay_after_query = 3                # Delay between API calls
  )

# View the number of records fetched
print(nrow(results))
head(results)
```

#### Fetch Records Without Dates

You can also fetch records missing the `main_date_str` field:

```{r message = FALSE, warning = FALSE}
# Fetch undated records
undated_records <- search_finna(
  query = "*",
  filters = c('collection:"VIO"', '-main_date_str:*'),
  limit = Inf
)

# View undated records
print(undated_records)
```

---

## Data Visualization

The Viola collection data can be visualized using metadata refinement and plotting functions.

#### Author Distribution

```{r message = FALSE, warning = FALSE, fig.alt = "viola author distribution"}
library(finna)
library(ggplot2)

# Refine metadata and visualize author distribution
refined_data <- refine_metadata(results)
top_plot(refined_data, field = "Year")
```






