---
title: "Viola in Finna"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Viola in Finna}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
This R Markdown document provides a comprehensive guide to querying and analyzing Viola collection data using the Finna API and the `fetch_viola_records` function.

## Viola Collection in Finna

The `fetch_viola_records` function allows batch processing of data from the Viola collection in Finna, across multiple year ranges, and handles records without date information.

### Example Usage

#### Fetch Data Across Year Ranges

The following example fetches data from the Viola collection for the year ranges: 0–1699, 1700–1799, and 1800–1899. 

```{r message = FALSE, warning = FALSE}
library(finna)

# Fetch records
results <- fetch_viola_records(
  base_query = "*",
  base_filters = c('collection:"VIO"'), # Filters for the Viola collection
  year_ranges = list(c(1700,1705)),           # Year ranges to query
  include_na = TRUE,                   # Include records with missing dates
  limit_per_query = 100000,              # Maximum records per query
  total_limit = Inf,                 # Overall record limit
  delay_after_query = 3                # Delay between API calls
  )

# View the number of records fetched
print(nrow(results))
head(results)
```

#### Fetch Records Without Dates

You can also fetch records missing the `main_date_str` field:

```{r message = FALSE, warning = FALSE}
# Fetch undated records
undated_records <- search_finna(
  query = "*",
  filters = c('collection:"VIO"', '-main_date_str:*'),
  limit = Inf
)

# View undated records
print(undated_records)
```

---

## Data Visualization

The Viola collection data can be visualized using metadata refinement and plotting functions.

#### Author Distribution

```{r message = FALSE, warning = FALSE, fig.alt = "viola author distribution"}
library(finna)

# Refine metadata and visualize author distribution
refined_data <- refine_metadata(results)
visualize_author_distribution(refined_data)
```

#### Word Cloud for Titles

```{r message = FALSE, warning = FALSE}
# Create a word cloud of titles
visualize_word_cloud(refined_data, "Title")
```




